surfing

### 2021-06-28 inst/surfing.Rmd
begin compatriot analysis

>>>>

# compatriot selection

```{r calculate_compatriot_monster_LF,cache=TRUE}
scomp <- hyper2()
for(v in o){
   r <- v[-1]  # first entry is venue
   numberretained <- sum(!(r %in% remove))
   if(numberretained > 1){
     r <- r[!(r %in% remove)]
     ## Now add a compatriot monster if needed

     if(numberretained ==3){
       nationalities <- c(nationality(r[1]),nationality(r[2]),nationality(r[3]))
       if(length(unique(nationalities)) == 2){
         print(nationalities)
         if(sum(nationality(r[1]) %in% nationalities) == 1){
           Hjj <- pwa(race(r),pwa=r[1])
	   print("a")
	   print(r)
	   print(nationalities)
	   print(Hjj)
         } else if(sum(nationality(r[2]) %in% nationalities) == 1){
           Hjj <- pwa(race(r),pwa=r[2])
	   print("b")
	   print(r)
	   print(nationalities)
	   print(Hjj)
         } else if(sum(nationality(r[3]) %in% nationalities) == 1){
	   Hjj <- pwa(race(r),pwa=r[3])
	   print("c")
	   print(r)
	   print(nationalities)
	   print(Hjj)
         } else {
           stop("this cannot happen")
         }
         scomp <- scomp + Hjj
       } else {  # no compatriot monster
         scomp <- scomp + race(r)
       }
     }
   }
}
```

```{r maximize_compatriot_monster,cache=TRUE}
maxs <- maxp(scomp)
maxs
```

```{r}
pie(maxs)
```

```{r testcompatriotmonster,cache=TRUE}
specificp.gt.test(scomp,"S",0)
```
